DRAFT Example Kitsap County Pedestrian Facilities Metrics/Evaluation Report

### 2022-10-03 Draft Ped Metrics Example.Rmd
change length in main document to st_length()

nice_comma <- function(x, dec = 0){
  format(round(as.numeric(x), dec), digits = NULL, nsmall=dec, big.mark=",") 
}
'%ni%' <- function(x,y)!('%in%'(x,y))

@@

# exclude Local Access EASEMENTS & Highway/Freeway
road_df <-st_as_sf(clean_roadcl) %>%
  filter(FCLASS %ni% c(100,110,1,2), RD_LOG_ID > 0)

ncdf <- road_df[!lengths(st_intersects(road_df, cities)), ]
#cdf <- st_intersection(road_df, cities)
#ncdf2 <- st_as_sf(road_df) %>%
#  mutate(rdseg = paste(SEGMENT_ID, RD_LOG_ID)) %>%
#  filter(rdseg %ni% mutate(cdf,rdseg = paste(SEGMENT_ID, RD_LOG_ID))$rdseg)
```

@@

sidewalks_nc <- sidewalks[!lengths(st_intersects(sidewalks, cities)), ]%>% 
  st_as_sf(.) %>%
  filter(WIDTH > 0, LENG_FT > 0) %>%
  mutate(LENGTH = LENG_FT,
         TYPE = paste0("Sidewalk: ",WIDTH, " ft"),
         RD_LOG_ID = as.integer(ROADLOGID),
         SEGMENT_ID = as.integer(SEG_ID)) %>%
  select(RD_LOG_ID,SEGMENT_ID,BMP,EMP,SIDE_OF_RO, WIDTH, LENGTH, TYPE)
shoulders_nc <- shoulders[!lengths(st_intersects(shoulders, cities)), ] %>% 
  st_as_sf(.) %>%
  filter(SHLDR_WIDT > 0, SHLDR_SURF == "ACP", DISTANCE_F > 0) %>%
  mutate(LENGTH = DISTANCE_F,
         TYPE = paste0("Paved Shoulder: ", SHLDR_WIDT," ft"),
         RD_LOG_ID = as.integer(ROAD_LOG_I),
         SEGMENT_ID = as.integer(SEG_ID)) %>%
  select(RD_LOG_ID,SEGMENT_ID,BMP,EMP,SIDE_OF_RO, WIDTH = SHLDR_WIDT, LENGTH, TYPE)
nc_sw_sh <- bind_rows(sidewalks_nc, shoulders_nc)

@@

```{r, cache = TRUE}
library(tidyverse)
library(sf)
kitsap_all_roads <- kitsap +
  geom_sf(data = clean_roadcl, aes(color = road_class)) + 
  road_col +
  theme_void() +
  labs(title = "Roads in Kitsap County",
       subtitle = paste0(nice_comma(sum(clean_roadcl$LENGTH)/5280),
                         " centerline miles"),
       #caption = "Data source: Kitsap GIS",
       color = "")

kitsap_roads_no_cities <- kitsap + 
  geom_sf(data = cities["NAME"], 
          aes(fill="NAME"),
          fill="#808080",
          alpha = 0.5,
          show.legend = FALSE) +
  geom_sf(data = ncdf, aes(color = road_class), show.legend = FALSE) + 
  road_col +
  theme_void() +
  labs(title = "No Cities, Easements, & Highways",
       subtitle = paste0(nice_comma(sum(ncdf$LENGTH)/5280),
                         " centerline miles"),
       caption = "Data source: Kitsap GIS")

@@

All of the data sets appear to use the same set of road log IDs from public works. Unfortunately, knowing that there is a shoulder or sidewalk somewhere on a road does not get to how much of that road has the sidewalk or shoulder.

>>>>

nice_comma <- function(x, dec = 1){
  format(round(as.numeric(x), dec), digits = NULL, nsmall=dec, big.mark=",") 
}
'%ni%' <- function(x,y)!('%in%'(x,y))

@@

# exclude Local Access EASEMENTS & Highway/Freeway
road_df <-st_as_sf(clean_roadcl) %>%
  filter(FCLASS %ni% c(100,110,1,2), RD_LOG_ID > 0) %>%
  mutate(LENGTH = st_length(.))

ncdf <- road_df[!lengths(st_intersects(road_df, cities)), ] %>%
  mutate(LENGTH = st_length(.))

#cdf <- st_intersection(road_df, cities)
#ncdf2 <- st_as_sf(road_df) %>%
#  mutate(rdseg = paste(SEGMENT_ID, RD_LOG_ID)) %>%
#  filter(rdseg %ni% mutate(cdf,rdseg = paste(SEGMENT_ID, RD_LOG_ID))$rdseg)
```

@@

sidewalks_nc <- sidewalks[!lengths(st_intersects(sidewalks, cities)), ]%>% 
  st_as_sf(.) %>%
  filter(WIDTH > 0, LENG_FT > 0) %>%
  mutate(LENGTH = st_length(.),
         TYPE = paste0("Sidewalk: ",WIDTH, " ft"),
         RD_LOG_ID = as.integer(ROADLOGID),
         SEGMENT_ID = as.integer(SEG_ID)) %>%
  select(RD_LOG_ID,SEGMENT_ID,BMP,EMP,SIDE_OF_RO, WIDTH, LENGTH, TYPE)
shoulders_nc <- shoulders[!lengths(st_intersects(shoulders, cities)), ] %>% 
  st_as_sf(.) %>%
  filter(SHLDR_WIDT > 0, SHLDR_SURF == "ACP", DISTANCE_F > 0) %>%
  mutate(LENGTH = st_length(.),
         TYPE = paste0("Paved Shoulder: ", SHLDR_WIDT," ft"),
         RD_LOG_ID = as.integer(ROAD_LOG_I),
         SEGMENT_ID = as.integer(SEG_ID)) %>%
  select(RD_LOG_ID,SEGMENT_ID,BMP,EMP,SIDE_OF_RO, WIDTH = SHLDR_WIDT, LENGTH, TYPE)
nc_sw_sh <- bind_rows(sidewalks_nc, shoulders_nc)

@@

```{r, cache = TRUE}
library(tidyverse)
library(sf)
kitsap_all_roads <- kitsap +
  geom_sf(data = clean_roadcl, aes(color = road_class)) + 
  road_col +
  theme_void() +
  labs(title = "Roads in Kitsap County",
       subtitle = paste0(nice_comma(sum(st_length(clean_roadcl))/5280),
                         " centerline miles"),
       #caption = "Data source: Kitsap GIS",
       color = "")

kitsap_roads_no_cities <- kitsap + 
  geom_sf(data = cities["NAME"], 
          aes(fill="NAME"),
          fill="#808080",
          alpha = 0.5,
          show.legend = FALSE) +
  geom_sf(data = ncdf, aes(color = road_class), show.legend = FALSE) + 
  road_col +
  theme_void() +
  labs(title = "No Cities, Easements, & Highways",
       subtitle = paste0(nice_comma(sum(st_length(ncdf))/5280),
                         " centerline miles"),
       caption = "Data source: Kitsap GIS")

@@

All of the data sets appear to use the same set of road log IDs from public works. Unfortunately, knowing that there is a shoulder or sidewalk somewhere on a road does not get to how much of that road has the sidewalk or shoulder.^[As roads sometimes change names and road log IDs, there are also some breaks between the road data and sidewalk/shoulder data. This was noted for Madrone Ave in Manchester - given the same road log ID as Main St when the road bends.]
